Summarize twas: chr17 to 22

### 2020-08-05 analysis/index.Rmd
visual chr17to22

## Test veb_boost
A simplified version (mr.ash2): interative update of two mr.ash components

@@

>>>>

## Test mr.ash2s
A simplified version (mr.ash2) of `Veb_boost`: interative update of two mr.ash components

@@

  * [Using UKbiobank data (chr17 to 22), fusion weights Adipose subcutaneous](https://users.rcc.uchicago.edu/~simingz/simulation-mr.ash2s-ukbchr17to22-gtex.adipose.html)

### 2020-08-05 analysis/simulation-multi-ukbchr17to22-gtex.adipose_sa2_v2.Rmd
visual chr17to22

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
tags <- paste0('20200721-1-', 1:7)
tagglob <- '20200721-1-*'
tagextr <- '20200721-1-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
tags <- paste0('20200721-1-', c(2, 4:9))
tagglob <- '20200721-1-*'
tagextr <- '20200721-1-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```
